Untitled

### 2022-03-28 outputs/paper/paper.Rmd
import the data set and set uo the repo

---
title: "Untitled"
author: "Qiao Zhou"
date: "3/28/2022"
output: html_document
---

>>>>

---
title: "Untitled"
subtitle: "My subtitle if needed"
thanks: "Code and data are available at: LINK."
author: "Qiao Zhou"
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
